Probability

### 2016-04-21 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" resolve domain...

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}\in\Hilb$ induces
a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
space of events defined for any event $E\in\qevents$ as follows:
\[
\mu_\psi(E) = \ip{\psi}{E\psi}
\]
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$.

@@

\yutsung{I am going to verify if $\proj{\psi_{1}}+\proj{\psi_{2}}$
is a projection, then they are orthogonal. Given any state $\ket{\phi}=a\ket{\psi_{1}}+b\ket{\psi_{2}}$,
if $\proj{\psi_{1}}+\proj{\psi_{2}}$ is a projection, then 
\begin{eqnarray*}
\ket{\phi} & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\ket{\phi}\\
 & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\left(a\ket{\psi_{1}}+b\ket{\psi_{2}}\right)\\
 & = & a\ket{\psi_{1}}+b\ket{\psi_{2}}+a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
Therefore, we have 
\begin{eqnarray*}
0 & = & a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
However, $a$ and $b$ can be any numbers. Therefore, we must have
$0=\ip{\psi_{2}}{\psi_{1}}=\ip{\psi_{1}}{\psi_{2}}$.}
\end{itemize}
\yutsung{The following is the diagram for quantum probability objects
and their corresponding physical meaning (in parentheses): 
\[
\xymatrix{\textrm{projections (events)}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
}
\]
}

>>>>

We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
We first assume an ambient Hilbert space~$\Hilb$ and define the
set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\[
\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}
\]
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$.

@@

\yutsung{I am going to verify if $\proj{\psi_{1}}+\proj{\psi_{2}}$
is a projection, then they are orthogonal. Given any state $\ket{\phi}=a\ket{\psi_{1}}+b\ket{\psi_{2}}$,
if $\proj{\psi_{1}}+\proj{\psi_{2}}$ is a projection, then 
\begin{eqnarray*}
\ket{\phi} & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\ket{\phi}\\
 & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\left(a\ket{\psi_{1}}+b\ket{\psi_{2}}\right)\\
 & = & a\ket{\psi_{1}}+b\ket{\psi_{2}}+a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
Therefore, we have 
\begin{eqnarray*}
0 & = & a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
However, $a$ and $b$ can be any numbers. Therefore, we must have
$0=\ip{\psi_{2}}{\psi_{1}}=\ip{\psi_{1}}{\psi_{2}}$.}
\end{itemize}
